Palmer amaranth (\emph{Amaranthus palmeri}) adaptation to agroecossystems

### 2021-08-12 Manuscript/Manuscript.Rmd
oi

The model fit was 0.11, 0.14, 0.18 with using pseudo R squared test from McFadden, Cox and Snell, and Cragg and Uhler, respectively. The likelihood ratio test showed a p-value of < 0.00. The marginal effects showed that increasing a weight unit by 1 g increases the probability of having a female plant by 0.08%. Similar trend is observed to height as well as doy, whereas the probability of being female increase by 0.16% and 0.4% when a unit of height (cm) and day increases.

The model evaluation accuracy in the unseen 20% dataset was 0.61 with a cutoff value for female and male plants of 0.49. The model classification showed a precision of 0.59, recall of 0.76, and a F1 score of 0.66. In addition, the area under the curve was 0.61.

@@

Our study showed that Palmer amaranth flowering time, biomass and height varied within agroecossystems and cohort timing. In general, Palmer amaranth produced more biomass and taller plants when growing at first cohort rather than second cohort. At first cohort, resources (e.g., soil nutrients) and conditions (e.g., light) were more timely available for both species, crop and weed. High biomass and taller Palmer amaranth plants are likely a weed strategy to compete for light in between crop rows in absence of canopy. In such condition, Palmer amaranth showed an extraordinary plasticity to adapt upon the agroecosystem. This is evident when comparing Palmer amaranth shape, and its extended flowering pattern when growing into corn compared to soybean. Palmer amaranth was taller and thinner when growing within corn. The Palmer amaranth competition strategy was likely to mimic the crop grow and development (Figure 4). These results are concerning as breeding more competitive crop varieties is likely to select more competitive Palmer amaranth biotypes [@bravo2017].

@@

Seed production was not evaluated due to Palmer amaranth harvest at flowering time. Nonetheless, it is well documented a strong positive correlation between Palmer amaranth biomass and seed production [@schwartz2016; @spaunhorst2018]. I our study, Palmer amaranth growing at first cohort accumulated an overall 36% more biomass when compared to second cohort. Therefore, Palmer amaranth plants growing in the second cohort is likely to produce less seeds regardless the agroecossystem. Our observation is consistent with the findings that first Palmer amaranth cohort produced 50% more seeds per plant than Palmer amaranth plants established six weeks later in bareground [@webster2015]. Nonetheless, seed production at second cohort is likely to replenish the soil seedbank. Seed production and deposition in the seedbank is a key factor for species perpetuation [@menges1987]. Palmer amaranth can produce hundred thousands seeds per plant [@schwartz2016; @keeley1987], and stay viable buried in the seedbank for at least 36 months [@sosnoskie2013].

Palmer amaranth flowering pattern was slightly influenced by cropping systems and cohort timings. Palmer amaranth growing in fallow and corn resulted in the overall shortest and longest flowering pattern. When growing in soybean, Palmer amaranth flowering pattern was similar to bareground and corn agroecossystems at first and second cohort timings, respectively. It seems that Palmer amaranth cohorts tend to have an extended flowering pattern when in high competition. The agroecossystems influenced Palmer amaranth gender. When growing in corn, the probability of having Palmer amaranth female plants reduced 18.1%.

Our study demonstrated the short-term Palmer amaranth plasticity to grow and develop into cropping-systems. Palmer amaranth management priority should focus on minimizing Palmer amaranth dispersal into new geographies. Early-season management programs would have a large negative effect in Palmer amaranth growth and development. Tactics that promote early-season crop advantage against Palmer amaranth, including early crop planting, crop rotation, plant width, preemergence applied herbicide [@sanctis2021], and crop residue (e.g. cover crops) would minimize the negative impact of Palmer amaranth in agroecossystems.

>>>>

The model fit was 0.11, 0.14, 0.18 with using pseudo R squared test from McFadden, Cox and Snell, and Cragg and Uhler, respectively. The likelihood ratio test showed a p-value of < 0.00. The average marginal effects showed that increasing a weight unit by 1 g increases the probability of having a female plant by 0.08% (P = 0.01). Similar trend is observed to height as well as doy, whereas the probability of being female increase by 0.2% (P = 0.01) and 0.4% (P = 0.00) when a unit of height (cm) and day increases, respectively.

The model accuracy evaluation accuracy in the unseen 20% dataset was 0.61 with a cutoff value for female and male plants of 0.49. The model classification showed a precision of 0.59, recall of 0.76, and a F1 score of 0.66. In addition, the area under the curve was 0.61.

@@

Our study showed that Palmer amaranth biomass, height, flowering pattern and gender varied within agroecossystems and cohort timings. In general, Palmer amaranth produced more biomass and taller plants when growing at first cohort rather than second cohort. At first cohort, resources (e.g., soil nutrients) and conditions (e.g., light) were more timely available for both species, crop and weed. High biomass and taller Palmer amaranth plants are likely a weed strategy to compete for light in between crop rows in absence of canopy. In such condition, Palmer amaranth showed an extraordinary plasticity to adapt upon the agroecosystem. This is evident when comparing Palmer amaranth canopy shape, and its extended flowering pattern when growing into corn compared to soybean. Palmer amaranth was taller and thinner when growing within corn. The Palmer amaranth competition strategy was to mimic the crop grow and development (Figure 4). These results suggests that Palmer amaranth can fast evolve life-history traits to adapt  into agroecossystems and cultural practices, including nitrogen fertilization [@bravo2018]. Our result highlight the threat of Palmer amaranth to agroecossystems as breeding more competitive crop varieties is likely to select more competitive biotypes [@bravo2017].

@@

Seed production was not evaluated due to plant harvest at initiation of flowering. Nonetheless, it is well documented a strong positive correlation between Palmer amaranth biomass and seed production [@schwartz2016; @spaunhorst2018]. I our study, Palmer amaranth growing at first cohort accumulated an overall 36% more biomass when compared to second cohort. Therefore, Palmer amaranth plants growing in the second cohort is likely to produce less seeds regardless the agroecossystem. Our observation is consistent with the findings that first Palmer amaranth cohort produced 50% more seeds per plant than Palmer amaranth plants established six weeks later in bareground [@webster2015]. Still, seed production at second cohort is likely to replenish the soil seedbank. Seed production and deposition in the seedbank is also a key factor for species perpetuation [@menges1987]. Palmer amaranth can produce hundred thousands seeds per plant [@schwartz2016; @keeley1987], and stay viable buried in the seedbank for at least 36 months [@sosnoskie2013]. Therefore, avoid Palmer amaranth seed production is also a key strategy to minimize weed impact into agroecossystems.

An ecological approach to reduce seed production in Palmer amaranth is understanding its flowering pattern. Our study suggests that Palmer amaranth flowering pattern was slightly influenced by cropping systems and cohort timings. Palmer amaranth growing in fallow and corn resulted in the overall shortest and longest flowering pattern, respectively. When growing in soybean, Palmer amaranth flowering pattern was similar to bareground at first cohort but similar to corn at second cohort timing. Plant flowering initiation is complex and depends on biological and ecological factors [@lang1965]. We hypothesize that when growing in high competition (e.g., second cohort), Palmer amaranth plants tend to initiate flowering early, as well as having an extended flowering pattern. Early flower initiation is plant strategy when growing under stress. For example, when growing under water stress, early flowering in Palmer amaranth resulted in a mismatch between female and male plants by seven days [@mesgaran2021]. A mismatch in Palmer amaranth male and female flowering period can minimize plant outcross, and thus reduce plant seed production. Sex dimorphism manipulation is considered a potential ecological pest control [@mcfarlane2018; @schliekelman2005].

The mechanisms of sex-determination in plant species is intriguing and arouse the curiosity of many scientists, including Darwin [@darwin1888]. In our study, the gender model performance was decent considering the biology of plant flowering. A 1:1 male and female sex ratio is a general evolutionary stable strategy for plant species perpetuation [@fisher1930]. However, a slight deviation from 1:1 sex ratio might occur in some dioecious species. For example, the dioecious *Halophila stipulacea* is a female-biased plant in its native habitat, but the naturalized *H. stipulacea* have a 1:1 ratio [@nguyen2018]. Naturalized of *H. stipulacea* reduced female-male ratio to expand into its non-native habitat. Also, biotic and/or abiotic stress can influence plant sex determination. Palmer amaranth  male-to-female ratio was greater under high plant densities [@korres2017a] and after herbicide application [@rumpa2019]. Our model estimated that late flowering, heavier and taller Palmer amaranth plants deviated from 1:1 ratio in favor to female plants. It was reported that female Palmer amaranth plants invested more in height, stem and biomass while male invested more in leaf area and leaf dry weight under nutrient deficiency [@korres2017]. Our model also estimated more female plants in soybean and bareground compared to corn, which might be a result of plant biomass in each agroecossystem. Our results showed the influence of life-history and ecological traits on sexual dimorphism in Palmer amaranth. Sexual dimorphism is documented in other dioecious species [@barrett2013]. For example, stronger female plant competition and greater male tolerance to herbivory was reported in *Spinacia oleracea* [@perez-llorca2019]. Research on candidate genes for sex determination in *Amaranthus* species are currently underway but it is far to complete [@montgomery2021; @montgomery2019]. Further studies are also needed to understand the ecological basis of Palmer amaranth flowering.

Our study demonstrated the short-term Palmer amaranth plasticity to grow and develop into cropping-systems. Palmer amaranth management priority should focus on minimizing Palmer amaranth dispersal into new geographies. Flower manipulation is a promising ecological Palmer amaranth but it is not well understood. Nonetheless, early-season management programs would have a large negative effect in Palmer amaranth growth and development. Tactics that promote early-season crop advantage against Palmer amaranth, including early crop planting, crop rotation [@oliveira2021a], plant width, preemergence applied herbicide [@sanctis2021], and crop residue (e.g. cover crops) would minimize the negative impact of Palmer amaranth in agroecossystems.

### 2021-08-12 Manuscript/Manuscript.tex
oi

The model fit was 0.11, 0.14, 0.18 with using pseudo R squared test from
McFadden, Cox and Snell, and Cragg and Uhler, respectively. The
likelihood ratio test showed a p-value of \textless{} 0.00. The marginal
effects showed that increasing a weight unit by 1 g increases the
probability of having a female plant by 0.08\%. Similar trend is
observed to height as well as doy, whereas the probability of being
female increase by 0.16\% and 0.4\% when a unit of height (cm) and day
increases.

The model evaluation accuracy in the unseen 20\% dataset was 0.61 with a
cutoff value for female and male plants of 0.49. The model
classification showed a precision of 0.59, recall of 0.76, and a F1
score of 0.66. In addition, the area under the curve was 0.61.

@@

Our study showed that Palmer amaranth flowering time, biomass and height
varied within agroecossystems and cohort timing. In general, Palmer
amaranth produced more biomass and taller plants when growing at first
cohort rather than second cohort. At first cohort, resources (e.g., soil
nutrients) and conditions (e.g., light) were more timely available for
both species, crop and weed. High biomass and taller Palmer amaranth
plants are likely a weed strategy to compete for light in between crop
rows in absence of canopy. In such condition, Palmer amaranth showed an
extraordinary plasticity to adapt upon the agroecosystem. This is
evident when comparing Palmer amaranth shape, and its extended flowering
pattern when growing into corn compared to soybean. Palmer amaranth was
taller and thinner when growing within corn. The Palmer amaranth
competition strategy was likely to mimic the crop grow and development
(Figure 4). These results are concerning as breeding more competitive
crop varieties is likely to select more competitive Palmer amaranth
biotypes (Bravo et al., 2017).

Palmer amaranth grow and development at second cohort was limited due to
the crop competitive ability at advanced development stages. Palmer
amaranth was transplanted when corn canopy was nearly closed, which
reduced Palmer amaranth competitiveness. As a result, Palmer amaranth
height and biomass was lower compared to its first cohort. Under crop
canopy, Palmer amaranth flowering pattern was near to similar in corn
and soybean. Palmer amaranth growing without crop competition produced
highest amounts of biomass and less extended flowering pattern. The
Palmer amaranth strategy in bareground was to invest biomass in growing
plant width and height. Nonetheless, Palmer amaranth produced 31\% less
biomass in second cohort compared to first cohort timing. In a
bareground study, early emerged Palmer amaranth without competition was
50\% taller than late emerged plants (Webster and Grey, 2015). These
results suggests that crop competition is not the only factor limiting
late Palmer amaranth establishment. The limited growth of Palmer
amaranth at second cohort is likely a reduced plant response to thermal
units (e.g, growing degree days). It is hypothesize that reduced day
length contributed to smaller plants at second cohort as well as shorter
flowering period. A study in North Carolina and Illinois predicted that
less than 10\% Palmer amaranth seedlings emergence occurred after June
(Piskackova et al., 2021). In addition, Palmer amaranth negative impact
on soybean (Korres et al., 2020) and cotton (Webster and Grey, 2015)
yields was higher when plants were established near to crop planting.

Seed production was not evaluated due to Palmer amaranth harvest at
flowering time. Nonetheless, it is well documented a strong positive
correlation between Palmer amaranth biomass and seed production
(Schwartz et al., 2016; Spaunhorst et al., 2018). I our study, Palmer
amaranth growing at first cohort accumulated an overall 50\% more
biomass when compared to second cohort. Therefore, Palmer amaranth
plants growing in the second cohort is likely to produce less seeds
regardless the agroecossystem. Our observation is consistent with the
findings that first Palmer amaranth cohort produced 50\% more seeds per
plant than Palmer amaranth plants established six weeks later in
bareground (Webster and Grey, 2015). Nonetheless, seed production at
second cohort is likely to replenish the soil seedbank. Seed production
and deposition in the seedbank is a key factor for species perpetuation
(Menges, 1987). Palmer amaranth can produce hundred thousands seeds per
plant (Schwartz et al., 2016; Keeley et al., 1987), and stay viable
buried in the seedbank for at least 36 months (Sosnoskie et al., 2013).

Palmer amaranth flowering pattern was variable

Our study demonstrated the short-term Palmer amaranth plasticity to grow
and develop into cropping-systems. Palmer amaranth management priority
should focus on minimizing Palmer amaranth dispersal into new
geographies. Early-season management programs would have a large
negative effect in Palmer amaranth growth and development. Tactics that
promote crop advantage against Palmer amaranth, including early crop
planting, crop rotation, plant width, preemergence applied herbicide
(Sanctis et al., 2021), and crop residue (e.g.~cover crops) would
minimize the negative impact of Palmer amaranth in agroecossystems.

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

The model fit was 0.11, 0.14, 0.18 with using pseudo R squared test from
McFadden, Cox and Snell, and Cragg and Uhler, respectively. The
likelihood ratio test showed a p-value of \textless{} 0.00. The average
marginal effects showed that increasing a weight unit by 1 g increases
the probability of having a female plant by 0.08\% (P = 0.01). Similar
trend is observed to height as well as doy, whereas the probability of
being female increase by 0.2\% (P = 0.01) and 0.4\% (P = 0.00) when a
unit of height (cm) and day increases, respectively.

The model accuracy evaluation accuracy in the unseen 20\% dataset was
0.61 with a cutoff value for female and male plants of 0.49. The model
classification showed a precision of 0.59, recall of 0.76, and a F1
score of 0.66. In addition, the area under the curve was 0.61.

@@

Our study showed that Palmer amaranth biomass, height, flowering pattern
and gender varied within agroecossystems and cohort timings. In general,
Palmer amaranth produced more biomass and taller plants when growing at
first cohort rather than second cohort. At first cohort, resources
(e.g., soil nutrients) and conditions (e.g., light) were more timely
available for both species, crop and weed. High biomass and taller
Palmer amaranth plants are likely a weed strategy to compete for light
in between crop rows in absence of canopy. In such condition, Palmer
amaranth showed an extraordinary plasticity to adapt upon the
agroecosystem. This is evident when comparing Palmer amaranth canopy
shape, and its extended flowering pattern when growing into corn
compared to soybean. Palmer amaranth was taller and thinner when growing
within corn. The Palmer amaranth competition strategy was to mimic the
crop grow and development (Figure 4). These results suggests that Palmer
amaranth can fast evolve life-history traits to adapt into
agroecossystems and cultural practices, including nitrogen fertilization
(Bravo et al., 2018). Our result highlight the threat of Palmer amaranth
to agroecossystems as breeding more competitive crop varieties is likely
to select more competitive biotypes (Bravo et al., 2017).

Palmer amaranth grow and development at second cohort was limited due to
the crop competitive ability at advanced development stages. Palmer
amaranth was transplanted when corn canopy was nearly closed, which
reduced Palmer amaranth competitiveness. As a result, Palmer amaranth
height and biomass was lower compared to its first cohort. Under crop
canopy, Palmer amaranth flowering pattern was near to similar in corn
and soybean. Palmer amaranth growing without crop competition produced
highest amounts of biomass and less extended flowering pattern. The
Palmer amaranth strategy in bareground was to invest biomass in growing
plant width and height. Nonetheless, Palmer amaranth produced 21\% less
biomass in second cohort compared to first cohort timing. In a
bareground study, early emerged Palmer amaranth without competition was
50\% taller than late emerged plants (Webster and Grey, 2015). These
results suggests that crop competition is not the only factor limiting
late Palmer amaranth establishment. The limited growth of Palmer
amaranth at second cohort is likely a reduced plant response to thermal
units (e.g, growing degree days). It is hypothesize that reduced day
length contributed to smaller plants at second cohort as well as shorter
flowering period. A study in North Carolina and Illinois predicted that
less than 10\% Palmer amaranth seedlings emergence occurred after June
(Piskackova et al., 2021). In addition, Palmer amaranth negative impact
on soybean (Korres et al., 2020) and cotton (Webster and Grey, 2015)
yields was higher when plants were established near to crop planting.

Seed production was not evaluated due to plant harvest at initiation of
flowering. Nonetheless, it is well documented a strong positive
correlation between Palmer amaranth biomass and seed production
(Schwartz et al., 2016; Spaunhorst et al., 2018). I our study, Palmer
amaranth growing at first cohort accumulated an overall 36\% more
biomass when compared to second cohort. Therefore, Palmer amaranth
plants growing in the second cohort is likely to produce less seeds
regardless the agroecossystem. Our observation is consistent with the
findings that first Palmer amaranth cohort produced 50\% more seeds per
plant than Palmer amaranth plants established six weeks later in
bareground (Webster and Grey, 2015). Still, seed production at second
cohort is likely to replenish the soil seedbank. Seed production and
deposition in the seedbank is also a key factor for species perpetuation
(Menges, 1987). Palmer amaranth can produce hundred thousands seeds per
plant (Schwartz et al., 2016; Keeley et al., 1987), and stay viable
buried in the seedbank for at least 36 months (Sosnoskie et al., 2013).

Palmer amaranth flowering pattern was slightly influenced by cropping
systems and cohort timings. Palmer amaranth growing in fallow and corn
resulted in the overall shortest and longest flowering pattern,
respectively. When growing in soybean, Palmer amaranth flowering pattern
was similar to bareground at first cohort but similar to corn at second
cohort timing. Plant flowering initiation is complex and depends on
biological and ecological factors (Lang, 1965). We hypothesize that when
growing in high competition (e.g., second cohort), Palmer amaranth
plants tend to initiate flowering early, as well as having an extended
flowering pattern. Early flower initiation is plant strategy when
growing under stress. For example, when growing under water stress,
early flowering in Palmer amaranth resulted in a mismatch between female
and male plants by seven days (Mesgaran et al., 2021). A mismatch in
Palmer amaranth male and female flowering period can minimize plant
outcross, and thus reduce plant seed production.

The gender model performance was decent considering the biology of plant
flowering. A 1:1 male and female sex ratio is a general evolutionary
stable strategy for plant species perpetuation (Fisher, 1930). However,
a slight deviation from 1:1 sex ratio might occur in some dioecious
species. For example, the dioecious \emph{Halophila stipulacea} is a
female-biased plant in its native habitat, but the naturalized \emph{H.
stipulacea} have a 1:1 ratio (Nguyen et al., 2018). Naturalized of
\emph{H. stipulacea} reduced female-male ratio to expand into its
non-native habitat. Also, biotic and/or abiotic stress can influence
plant sex determination. Palmer amaranth male-to-female ratio was
greater under high plant densities (Korres and Norsworthy, 2017) and
after herbicide application (Rumpa et al., 2019). Our model estimated
that late flowering, heavier and taller Palmer amaranth plants deviated
from 1:1 ratio in favor to female plants. It was reported that female
Palmer amaranth plants invested more in height, stem and biomass while
male invested more in leaf area and leaf dry weight under nutrient
deficiency (Korres et al., 2017). Our model also estimated more female
plants in soybean and bareground compared to corn, which might be a
result of plant biomass in each agroecossystem. Our results showed the
influence of life-history and ecological traits on sexual dimorphism in
Palmer amaranth. Sexual dimorphism is documented in other dioecious
species (Barrett and Hough, 2013). For example, stronger female plant
competition and greater male tolerance to herbivory was reported in
\emph{Spinacia oleracea} (Pérez-Llorca and Sánchez Vilas, 2019). The
mechanisms of sex-determination in plant species is intriguing and
arouse the curiosity of many scientists, including Darwin (Darwin,
1888). Research on candidate genes for sex determination in
\emph{Amaranthus} species are currently underway (Montgomery et al.,
2021, 2019). Sex dimorphism manipulation is considered a potential
ecological pest control (McFarlane et al., 2018; Schliekelman et al.,
2005).

Our study demonstrated the short-term Palmer amaranth plasticity to grow
and develop into cropping-systems. Palmer amaranth management priority
should focus on minimizing Palmer amaranth dispersal into new
geographies. Early-season management programs would have a large
negative effect in Palmer amaranth growth and development. Tactics that
promote early-season crop advantage against Palmer amaranth, including
early crop planting, crop rotation, plant width, preemergence applied
herbicide (Sanctis et al., 2021), and crop residue (e.g.~cover crops)
would minimize the negative impact of Palmer amaranth in
agroecossystems.

@@

\leavevmode\hypertarget{ref-barrett2013}{}%
Barrett, S. C. H., and Hough, J. (2013). Sexual dimorphism in flowering
plants. \emph{Journal of Experimental Botany} 64, 67--82.
doi:\href{https://doi.org/10.1093/jxb/ers308}{10.1093/jxb/ers308}.

@@

\leavevmode\hypertarget{ref-bravo2018}{}%
Bravo, W., Leon, R. G., Ferrell, J. A., Mulvaney, M. J., and Wood, C. W.
(2018). Evolutionary {Adaptations} of {Palmer Amaranth} ({Amaranthus}
palmeri) to {Nitrogen Fertilization} and {Crop Rotation History Affect
Morphology} and {Nutrient}-{Use Efficiency}. \emph{Weed Science} 66,
180--189.
doi:\href{https://doi.org/10.1017/wsc.2017.73}{10.1017/wsc.2017.73}.

@@

\leavevmode\hypertarget{ref-darwin1888}{}%
Darwin, C. (1888). \emph{The {Different Forms} of {Flowers} on {Plants}
of the {Same Species}}. {J. Murray} Available at:
\url{http://books.google.com?id=7uMEAAAAYAAJ}.

@@

\leavevmode\hypertarget{ref-fisher1930}{}%
Fisher, R. A. (1930). The genetical theory of natural selection.
\emph{Eugen Rev} 22, 127--130. Available at:
\url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2984947/} {[}Accessed
August 12, 2021{]}.

@@

\leavevmode\hypertarget{ref-korres2017a}{}%
Korres, N. E., and Norsworthy, J. K. (2017). Palmer {Amaranth}
({Amaranthus} palmeri) {Demographic} and {Biological Characteristics} in
{Wide}-{Row Soybean}. \emph{Weed Science} 65, 491--503.
doi:\href{https://doi.org/10.1017/wsc.2017.12}{10.1017/wsc.2017.12}.

\leavevmode\hypertarget{ref-korres2017}{}%
Korres, N. E., Norsworthy, J. K., FitzSimons, T., Roberts, T. L., and
Oosterhuis, D. M. (2017). Differential {Response} of {Palmer Amaranth}
({Amaranthus} palmeri) {Gender} to {Abiotic Stress}. \emph{Weed Science}
65, 213--227.
doi:\href{https://doi.org/10.1017/wsc.2016.34}{10.1017/wsc.2016.34}.

@@

\leavevmode\hypertarget{ref-lang1965}{}%
Lang, A. (1965). {``Physiology of flower initiation,''} in
\emph{Differenzierung und {Entwicklung} / {Differentiation} and
{Development}} Handbuch der {Pflanzenphysiologie} / {Encyclopedia} of
{Plant Physiology}., ed. A. Lang ({Berlin, Heidelberg}: {Springer}),
1380--1536.
doi:\href{https://doi.org/10.1007/978-3-642-50088-6_39}{10.1007/978-3-642-50088-6\_39}.

@@

\leavevmode\hypertarget{ref-mcfarlane2018}{}%
McFarlane, G. R., Whitelaw, C. B. A., and Lillico, S. G. (2018).
{CRISPR}-{Based Gene Drives} for {Pest Control}. \emph{Trends in
Biotechnology} 36, 130--133.
doi:\href{https://doi.org/10.1016/j.tibtech.2017.10.001}{10.1016/j.tibtech.2017.10.001}.

@@

\leavevmode\hypertarget{ref-mesgaran2021}{}%
Mesgaran, M. B., Matzrafi, M., and Ohadi, S. (2021). Sex dimorphism in
dioecious {Palmer} amaranth ({Amaranthus} palmeri) in response to water
stress. \emph{Planta} 254, 17.
doi:\href{https://doi.org/10.1007/s00425-021-03664-7}{10.1007/s00425-021-03664-7}.

@@

\leavevmode\hypertarget{ref-montgomery2021}{}%
Montgomery, J. S., Giacomini, D. A., Weigel, D., and Tranel, P. J.
(2021). Male-specific {Y}-chromosomal regions in waterhemp ({Amaranthus}
tuberculatus) and {Palmer} amaranth ({Amaranthus} palmeri). \emph{New
Phytologist} 229, 3522--3533.
doi:\href{https://doi.org/10.1111/nph.17108}{10.1111/nph.17108}.

\leavevmode\hypertarget{ref-montgomery2019}{}%
Montgomery, J. S., Sadeque, A., Giacomini, D. A., Brown, P. J., and
Tranel, P. J. (2019). Sex-specific markers for waterhemp ({Amaranthus}
tuberculatus) and {Palmer} amaranth ({Amaranthus} palmeri). \emph{Weed
Science} 67, 412--418.
doi:\href{https://doi.org/10.1017/wsc.2019.27}{10.1017/wsc.2019.27}.

@@

\leavevmode\hypertarget{ref-nguyen2018}{}%
Nguyen, H. M., Kleitou, P., Kletou, D., Sapir, Y., and Winters, G.
(2018). Differences in flowering sex ratios between native and invasive
populations of the seagrass {Halophila} stipulacea. \emph{Botanica
Marina} 61, 337--342.
doi:\href{https://doi.org/10.1515/bot-2018-0015}{10.1515/bot-2018-0015}.

@@

\leavevmode\hypertarget{ref-perez-llorca2019}{}%
Pérez-Llorca, M., and Sánchez Vilas, J. (2019). Sexual dimorphism in
response to herbivory and competition in the dioecious herb {Spinacia}
oleracea. \emph{Plant Ecol} 220, 57--68.
doi:\href{https://doi.org/10.1007/s11258-018-0902-7}{10.1007/s11258-018-0902-7}.

@@

\leavevmode\hypertarget{ref-rumpa2019}{}%
Rumpa, M. M., Krausz, R. F., Gibson, D. J., and Gage, K. L. (2019).
Effect of {PPO}-{Inhibiting Herbicides} on the {Growth} and {Sex Ratio}
of a {Dioecious Weed Species Amaranthus} palmeri ({Palmer Amaranth}).
\emph{Agronomy} 9, 275.
doi:\href{https://doi.org/10.3390/agronomy9060275}{10.3390/agronomy9060275}.

@@

\leavevmode\hypertarget{ref-schliekelman2005}{}%
Schliekelman, P., Ellner, S., and Gould, F. (2005). Pest {Control} by
{Genetic Manipulation} of {Sex Ratio}. \emph{Journal of Economic
Entomology} 98, 18--34.
doi:\href{https://doi.org/10.1093/jee/98.1.18}{10.1093/jee/98.1.18}.
